Liveness-Based Garbage Collection for Lazy Languages

### 2015-07-11 paper/paper.tex
typo

Table~\ref{tab:experimental-results}  compares the  garbage collection
statisctics for  RGC and LGC  with reachability for  copying closures.
We report the  number of GC events, average number  of cells reclaimed
per  GC, average  number  of cells  touched per  GC,  total number  of
dragged cells  and total time  to perform  all collections.  It  is no
surprise  that  number  of  cells  reclaimed per  GC  is  higher  (and
consequently the  number of  GCs is lower)  for LGC  based collection.
LGC also reduces  the number of dragged  cells significantly. However,
the cost for LGC is that per  GC execution time is more for LGC, which
results in higher overall execution  time for garbage collection, even
with reduced  number of collections.   However, LGC run time  is still
competitive (slowdown within 5X of RGC  for worst case), and is better
for   3    benchmarks   (best    case   2X   speedup).     Note   that
\verb@gc_bench@~\cite{gc_bench}   is  a   synthestic  benchmark   that
allocates complete binary  trees of various sizes.  These binary trees
are  never used  by the  program. As  a result,  the benchmark  highly
favours LGC.   We have included  this benchmark for  completeness only
and the numbers for it  are not considered representative of practical
programs.

@@

One area  of concern is the  huge gap between the  actual liveness and
the liveness  percieved by our  collector.  In  case of LGC  for eager
languages~\ref{asati14lgc} the gap was  very narrow and almost touched
the actual  liveness curve.  In  case of  lazy languages, this  gap is
largely   due  to   approximate  reachability   based  collection   of
closures. To implement liveness based  collection of closures, we need
to  record liveness  data  for  each closure  and  update  it at  each
evaluation  point.   These  space  and  run  time  overheads  make  it
infeasible  to  incorporate  liveness  based  GC  for  closures  in  a
practical garbage collector.

>>>>

Table~\ref{tab:experimental-results}  compares the  garbage collection
statistics for RGC and LGC  (with reachability for copying closures).
We report the  number of GC events, average number  of cells reclaimed
per  GC, average  number  of cells  touched per  GC,  total number  of
dragged cells  and total time  to perform  all collections.  It  is no
surprise  that  number  of  cells  reclaimed per  GC  is  higher  (and
consequently the  number of  GCs is lower)  for LGC  based collection.
LGC also reduces  the number of dragged  cells significantly. However,
the cost for LGC is that per  GC execution time is more for LGC, which
results in higher overall execution  time for garbage collection, even
with reduced  number of collections.   However, LGC run time  is still
competitive (slowdown within 5X of RGC  for worst case), and is better
for   3    benchmarks   (best    case   2X   speedup).     Note   that
\verb@gc_bench@~\cite{gc_bench}   is  a   synthestic  benchmark   that
allocates complete binary trees of  various sizes.  These binary trees
are  never used  by the  program. As  a result,  the benchmark  highly
favours LGC.   We have included  this benchmark for  completeness only
and the numbers for it  are not considered representative of practical
programs.

@@

One area  of concern is the  huge gap between the  actual liveness and
the liveness  percieved by our  collector.  In  case of LGC  for eager
languages~\cite{asati14lgc} the gap was  very narrow and almost touched
the actual  liveness curve.  In  case of  lazy languages, this  gap is
largely   due  to   approximate  reachability   based  collection   of
closures. To implement liveness based  collection of closures, we need
to  record liveness  data  for  each closure  and  update  it at  each
evaluation  point.   These  space  and  run  time  overheads  make  it
infeasible  to  incorporate  liveness  based  GC  for  closures  in  a
practical garbage collector.
